Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-01 Paper/paper.tex
first draft of text for S4

\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0.pdf}
\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR50_CI90_0.pdf}\\

@@

In Fig.~\ref{fig:TT_SNRThresholds_BHspin_BHmass_CI90_0} we take the case of
faily deformable neutron stars, with actual $\lambdans = 1500$ (left panel) and
$2000$ (right panel). In each case, we calculate the lowest SNR value $\rho_c$ 
in order
for the signal to have enough information that we can constrain $\dlambda$ below
$100\%$. Note that this is a modest requirement on constrainability of $\lambdans$.
In each panel of the figure, we show $\rho_c$ as a function of BH mass and spin.
% 
We immediately note that to fulfil this modest aim with a single observation, 
we need an SNR of $30$ or higher in each detector. Given we have that, we can 
bring $\dlambda$ below $100\%$ for the lowest BH masses and higher spins. To
attain the same for other values of BH parameters, we will need a very loud
signal with $\rho\gtrsim 50$.

% 
% 
% \subsection{Constraining the tidal deformability of the neutron star}\label{s2:measuring_lambda}
%

% As before we focus on binaries with mass-ratios $q=\{[2,3,4,5\}$, with the NS mass
% fixed at $1.35M_\odot$. We allow BH spin to take the values 
% $\chibh=\{-0.5,0,+0.5,+0.75\}$, and $\lambdans=\{500, 800, 1000\}$. For each of these
% parameter combinations, we inject a tidal-corrected waveform using the 
% Lackey et al~\cite{} model , and use MCMC with ensemble sampling to construct the 
% posterior probability distribution for different binary parameters with (a) BHBH
% templates, and (b) NSBH templates. We will discuss the results of (b) here.

\pagebreak
\newpage
\FloatBarrier

>>>>

\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR20_CI90_0.pdf}
\includegraphics[width=1.025\columnwidth]{plots/TTLambdaErrorCurves_BHspin_BHmass_SNR30_CI90_0.pdf}\\

@@

In Fig.~\ref{fig:TT_SNRThresholds_BHspin_BHmass_CI90_0} we take the case of
moderately deformable neutron stars, with actual $\lambdans = 1000$ (left 
panel) and $1500$ (right panel), and ask how loud such a signal will have
to be for us to put meaningful constraints on the tidal deformability of NSs.
In the left panel, as a function BH mass and spin, 
we show the lowest SNR value $\rho_c$ in order for the signal to have enough
information that we can constrain $\dlambda$ below $200\%$. Note that 
being able to constrain $\lambdans$ within a factor of $2$ interval 
(i.e. within $\pm 100\%$) is a fairly modest requirement. We find promising 
results, which suggest that there is a fairly wide range of BH spins, less
wide (but non-trivial) range of BH masses, within
which if we get a moderately loud NSBH signal with $\rho\approx 20$, we constrain
$\lambdans$ within a factor of $2$ interval (i.e. within $\pm 100\%$) around
the true value. While this is not very precise, it can possibly allow us to
rule out candidates for the equation of state of neutron star matter.
% 
If we want to constrain $\lambdans$ better with a single observation, however,
we need SNRs of $30$ or higher in each detector. This can be seen from the right
panel of Fig.~\ref{fig:TT_SNRThresholds_BHspin_BHmass_CI90_0}, which is similar
to the left but for a higher $\lambdans (=1500)$ system, with a more stringent
constraint requirement that $\lambdans$ be measured within a factor of $1$ of 
its true value (i.e. with $\pm 50\%$ errors, instead of $\pm 100\%$). Even for
the most conducive cases, we {\it need} the SNR to be above $30$ to reach our 
accuracy threshold (which is more than $3\times$ less likely to happen than
getting a signal with $\rho=20$).

Lastly, in Fig.~\ref{fig:TT_LambdaErrorCurves_BHspin_BHmass_CI90_0} we show the
conditions that BH parameters must fulfil beside having an SNR of $20$ (left 
panel) or $30$ (right panel), to obtain meaningful contraints on $\lambdans$.
At $\rho=20$, the left panel shows that we need high BH spins 
$\chibh\gtrsim +0.6$ and a very deformable NS with $\lambdans\geq 1500$, in 
order to put a factor of $2$ bound on $\lambdans$. At $\rho=30$, with
$\lambdans\gtrsim 1000$ and $\chibh\geq+0.6$ we can put a similar factor of
$2$ bound on $\lambdans$, but with $\chibh\sim+0.75$ and an extremely deformable
NS with $\lambdans=200$ one could even put a $\pm 50\%$ errorbar on 
$\lambdans$ measurement.

In summary, with a single moderately loud BHNS observation, we could constrain
the NS compactness parameter $\lambdans$ within $\pm 100\%$ of its true value.
To measure better with one observation, we will need to get lucky with signals
with $\rho\geq 30$ and high BH spins, or $\rho\geq 50$.

% \pagebreak
% \newpage
% \FloatBarrier
